\TOWRITE{ALL}{Proofread WP 1 Management pass 1}
\begin{draft}
\TOWRITE{PS (Work Package Lead)}{For WP leaders, please check the following (remove items
once completed)}
\begin{verbatim}
- [ ] have all the tasks in this Work Package a lead institution?
- [ ] have all deliverables in the WP a lead institution?
- [ ] do all tasks list all sites involved in them?
- [ ] does the table of sites and their PM efforts match lists of sites for each task?
      (each site from the table is listed in all relevant tasks, and no site is listed
      only in the table or only at some task)
\end{verbatim}
\end{draft}

\begin{workpackage}[id=education,wphases=0-48,swsites,
  title=Education and Dissemination,
  short=Education,
  lead=INSERM,
  CDSRM=3,
  % EGIRM=4,
  EPRM=TBC,
  INSERMRM=12,
  QSRM=4,
  SILRM=4,
  SRLRM=12,
  UIORM=12,
  UPSUDRM=12,
  WTTRM=4,
  XFELRM=8,
]
\begin{wpobjectives}
  The objective of this work package is to develop the community at the
  European scale, foster cross team collaboration, spread the
  expertise, and engage the greater community to participate in the
  definition and refinement of the requirements, and the implementation and use of the
  produced solutions. This includes:
 \begin{compactitem}
   \item ensure awareness of the results in the user community;
   \item Train researchers in best practices for open and reproducible science
   \item Educate the community on the value of open science
   \item Produce training and education material to disseminate the ability to do reproducible computational science using the tools we develop.
   \item Define individual exploitation plans;
 \end{compactitem}
\end{wpobjectives}

% Potential sources of inspiration: ODK's WP2 work package about dissemination:
% PDF: p.36 of https://github.com/OpenDreamKit/OpenDreamKit/raw/master/Proposal/proposal-www.pdf
% Sources: https://github.com/OpenDreamKit/OpenDreamKit/blob/master/Proposal/WorkPackages/DisseminationCommunityBuilding.tex

\begin{wpdescription}

Open science is entirely dependent on researchers adopting open practices.
In \TheProject, we are developing tools to facilitate these practices,
but they only work if researchers actually adopt them.
Going further, it is also clear that open science is not just of value 
to researchers: one of the largest benefits of open science is that it makes 
science accessible to the broader public who may not be members of the 
research community.

To this end, in addition to training researchers, we will also train the public in how to 
make use of the open science research and services facilitated by \TheProject.
This will be done through regular open dissemination and training workshops, as well as
by producing and maintaining material for online courses and documentation.

\TheProject will develop, through WP4, a number of applications and demonstrators that
will be disseminated in different ways.
We will also participate in the concertation activities,
consultations and other meetings and events of the European
E-Infrastructure projects.

All the code, documents, test and build infrastructure produced as
part of the project will be made available as open source.
Open access to all publications resulting from the project will be ensured.


\end{wpdescription}

\begin{tasklist}
% add tasks from task directory here
\input{tasks/website-general}
\input{tasks/training}
\input{tasks/online-resources}
\input{tasks/helpdesk}
\end{tasklist}




\begin{wpdelivs}
\begin{wpdeliv}[due=1,miles=startup,id=infrastructure,dissem=PU,nature=DEC,lead=SRL]
  {Some Deliverable}
\end{wpdeliv}

\end{wpdelivs}
\end{workpackage}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:

%  LocalWords:  workpackage wphases wpobjectives wpdescription pageref wpdelivs wpdeliv
%  LocalWords:  dissem mailinglists swrepository final-mgt-rep compactitem swsites ipr
%  LocalWords:  TOWRITE tasklist delivref
