\TOWRITE{ALL}{Proofread WP 1 Management pass 1}
\begin{draft}
\TOWRITE{PS (Work Package Lead)}{For WP leaders, please check the following (remove items
once completed)}
\begin{verbatim}
- [ ] have all the tasks in this Work Package a lead institution?
- [ ] have all deliverables in the WP a lead institution?
- [ ] do all tasks list all sites involved in them?
- [ ] does the table of sites and their PM efforts match lists of sites for each task?
      (each site from the table is listed in all relevant tasks, and no site is listed
      only in the table or only at some task)
\end{verbatim}
\end{draft}

\begin{workpackage}[id=ecosystem,wphases=0-48,swsites,
  title=Developing the Jupyter Ecosystem,
  short=Ecosystem,
  lead=QS,
  % EGIRM=4,
  % INSERMRM=4,
  EPRM=21,
  QSRM=20,
  SILRM=16,
  SRLRM=30,
  % UIORM=4,
  UPSUDRM=2,
  WTTRM=6,
  XFELRM=54,
  EPRM=20,
]
\begin{wpobjectives}
 \begin{compactitem}
   \item develop projects for creating open science services built out of Jupyter components and exploring new models for such services
   \item develop tools for interactive visualization in Jupyter
   \item develop workflows for data science using Jupyter software
 \end{compactitem}
\end{wpobjectives}

\begin{wpdescription}

Open source software in general, and Jupyter in particular,
is developed not as a monolithic application,
but rather as a collection of related components,
which can be assembled in numerous combinations to meet diverse needs.
The Jupyter community is no different.
Jupyter itself is composed of several projects,
but there are even more projects that build on top of Jupyter to create
things like cloud services or data pipelines.
The goal of \TheProject is to facilitate open science through Jupyter,
and this includes working with projects all around the Jupyter ecosystem.
We will focus this work package on developing
Jupyter ecosystem projects with an emphasis on open science.

repo2docker is a project for creating
reproducible environments in which Jupyter notebooks (and other user interfaces) can be run.
It reads a number of common formats to list required software packages,
and prepares a Docker container with those packages installed.
BinderHub is software for operating a web service using repo2docker,
which enables sharing of interactive and reproducible Jupyter (and Rstudio) environments on the web with a single link.
We will develop repo2docker and BinderHub further to meet the needs of the open science community.

Widgets are an extension to Jupyter, which can define new kinds of interactivity.
3D visualisation of data is important to many kinds of science,
and there is lots of room for development of the 3D visualisation landscape in Jupyter.

In addition to the interactive aspects of Jupyter,
notebooks can be used in a "workflows" style,
where job systems run analyses and produce reports,
either on a scheduled basis or triggered by events.
There is a great deal of interest in using notebooks in this way,
and much room for development of tools supporting workflows in data-driven open science.

\end{wpdescription}

\begin{tasklist}
% add tasks from task directory here
% \input{tasks/template}
\input{tasks/r2d-and-binder}
\input{tasks/xeus}
\input{tasks/widgets}
\input{tasks/reproducibility}
\input{tasks/teaching-tools}
\end{tasklist}


\begin{wpdelivs}
\begin{wpdeliv}[due=12,miles=startup,id=binder-guidelines,dissem=PU,nature=DEC,lead=XFEL]
  {Guidelines for Binder use to improve reproducibility of
  environments, based on existing technology such as repo2docker}
\end{wpdeliv}
\begin{wpdeliv}[due=12,miles=startup,id=teaching-report,dissem=PU,nature=R,lead=EP]
  {Study of the practices of using Jupyter for teaching and the needs to
  effectively manage classes and associated courses in the education community}
\end{wpdeliv}
\begin{wpdeliv}[due=36,miles=community,id=nbgrader-like,dissem=PU,nature=OTHER,lead=EP]
  {Unified framework to effectively manage classes and associated courses
  using Jupyter technology}
\end{wpdeliv}
\begin{wpdeliv}[due=36,miles=community,id=jupyter-archive,dissem=PU,nature=OTHER,lead=XFEL]
  {Long-term reproducibility: Computational environment software
    archive system that extends lifetime of computational environments
  used in Binder service. TODO: Fix milestone}
\end{wpdeliv}
\begin{wpdeliv}[due=36,miles=community,id=k3d-jupyter,dissem=PU,nature=OTHER,lead=SIL]
  {Implement interoperable 3d visualization widget based on K3D-jupyter code}
\end{wpdeliv}


\end{wpdelivs}
\end{workpackage}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:

%  LocalWords:  workpackage wphases wpobjectives wpdescription pageref wpdelivs wpdeliv
%  LocalWords:  dissem mailinglists swrepository final-mgt-rep compactitem swsites ipr
%  LocalWords:  TOWRITE tasklist delivref
