\begin{participant}[type=leadPI,PM=4,gender=male]{Hans Fangohr}
  % type is one of:
  % - leadPI: leader of the participating institution
  % - PI: Principal Investigator
  % - R: researcher?
  % Who is the coordinator is specified elsewhere

  % PM=YYY:
  % A fair evaluation of the number of months you will be
  % spending on this specific project along the four years.
  % Typical numbers:
  % - full time hired personnel: 48 months
  % - lead PI or proposal coordinator: 8-12 months
  % - PI: 4-5 months
  % - participant: 2-6 months

  % salary=ZZZ:
  % Approximate monthly gross salary (in term of total cost for the
  % employer). This is optional. If you are uncomfortable having this
  % information in a public file, you can alternatively send the
  % information to Eugenia Shadlova, or to your institution
  % leader/manager if he is willing to fill in himself the budget
  % forms on the eu portal.

  % The above information is used to fill in various tables in the
  % proposal file, and to evaluate the cost of the project for the
  % institutions.

  % You may remove all those comments.

  % About half a page of free text; for whatever it's worth, you may see
  % Nicolas.Thiery.tex for an example.



  \medskip Hans Fangohr is an academic at the University
  of Southampton in the United Kingdom since 2002 (full professor
  since 2010), and leading the data analysis services at European XFEL
  in Germany since 2017.

  He has been a long term proponent of Open Science, and in particular
  involved with the the use and further development of the Jupyter
  Notebook to enable this. He has hosted Thomas Kluyver at the
  University of Southampton since 2015 from where he contributed as a
  core developer of the Jupyter team. As a PI in the EC-funded e-INFRA
  OpenDreamKit project (2015-2019), he has pushed forward the use of
  Jupyter Notebooks for reproducible computational science, and
  started the notebook validation tool (NBVAL). He made use of the
  Jupyter Ecosystem for research and education at graduate and
  postgraduate level at the University of Southampton, and shared
  resources widely, including a text book provided through Jupyter
  Notebooks, which can be executed interactively online [1].

  Since 2017, he is designing data analysis services and
  infrastructure at the European XFEL research facility. European XFEL
  is using IPython and the Jupyter Notebook as core utilities in their
  large scale experiment control, data capture and data
  analysis. Within the e-INFRA project PaNOSC (Photon and Neutron
  Science Open Cloud, 2018-2021), he is leader of the Work Package 4,
  which is focused on data analysis services for the EOSC Hub, and the
  use of the Jupyter notebook with its existing features on the EOSC
  hub.

  In this project (BOSSEE), where new capabilities for the Jupyter
  notebook and ecosystem are being designed, Hans' wide experience and
  interaction with different science groups will be beneficial to
  ensure the outcome is of value to open science in many domains. This
  includes him chairing the interdisciplinary computational modelling
  group at the University of Southampton (200 academics, 2008-2017),
  chairing the national EPSRC scientific advisory committee on High
  Performance Computing in the UK (2014-2017) and interacting with a
  large variety of science users at European XFEL in his role
  to lead the data analysis service provision.
\end{participant}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:
