\begin{participant}[type=PI,PM=28,gender=male]{Benjamin Ragan-Kelley}
  % PM=YYY:
  % A fair evaluation of the number of months you will be
  % spending on this specific project along the four years.
  % Typical numbers:
  % - full time hired personnel: 48 months
  % - lead PI or proposal coordinator: 8-12 months
  % - PI: 4-5 months
  % - participant: 2-6 months

  % salary=ZZZ:
  % Approximate monthly gross salary (in term of total cost for the
  % employer). This is optional. If you are uncomfortable having this
  % information in a public file, you can alternatively send the
  % information to Eugenia Shadlova, or to your institution
  % leader/manager if he is willing to fill in himself the budget
  % forms on the eu portal.

Benjamin Ragan-Kelley is one of the core maintainers and developers
of the Jupyter and IPython projects, and currently leads the JupyterHub
and BinderHub development teams.
He has been a contributor to these projects since 2006,
prior to the establishment of Jupyter as a separate project from IPython.
He is an expert in all levels of Jupyter development,
especially the aspects of deploying Jupyter-based services,
which is the focus of this proposal.
Benjamin will lead \TheProject.

Beyond Jupyter, Benjamin has contributed widely to open source software,
especially in the scientific Python community.
He is a maintainer of numerous scientific packages
in the conda-forge package management system,
building packages used widely in education and research,
such as PETSc, MPICH, and FEniCS.

Benjamin is a Research Engineer in the department of Scientific Computing and Numerical Analysis
at Simula Research Laboratory in Oslo, Norway,
where his primary responsibility is developing and maintaining the Jupyter software ecosystem,
as well as supporting research scientists in diverse fields,
including biomedical computing.

Prior to his current position at Simula,
Benjamin received his Bachelor's degree \textit{Magne cum Laude} in Engineering Physics in 2007
from Santa Clara University and his PhD in Applied Science and Technology
from the University of California, Berkeley in 2013.
He worked as a postdoctoral fellow at Simula Research Laboratory prior
to becoming a permanent Research Engineer.
He was honored along with the rest of the Jupyter steering council
with the 2017 ACM Software System Award for Jupyter.


\end{participant}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:
