\begin{participant}[type=R,PM=48,gender=male]{Thomas Kluyver}
  % PM=YYY:
  % A fair evaluation of the number of months you will be
  % spending on this specific project along the four years.
  % Typical numbers:
  % - full time hired personnel: 48 months
  % - lead PI or proposal coordinator: 8-12 months
  % - PI: 4-5 months
  % - participant: 2-6 months

  % salary=ZZZ:
  % Approximate monthly gross salary (in term of total cost for the
  % employer). This is optional. If you are uncomfortable having this
  % information in a public file, you can alternatively send the
  % information to Eugenia Shadlova, or to your institution
  % leader/manager if he is willing to fill in himself the budget
  % forms on the eu portal.
  Thomas Kluyver is one of the core maintainers of the Jupyter and IPython
  projects, which form a central part of this proposal.
  He has been part of the core IPython development team since 2011,
  before Jupyter was split out as a separate project.
  He is closely familiar with key parts of the code, and was one of
  15 core developers to receive the 2017 ACM Software System Award.

  Besides Jupyter, Thomas has contributed to a wide range of open source
  software projects in the Python ecosystem, ranging from other scientific
  computing tools such as h5py to packaging utilities such as Flit, as well
  as improvements in the Python standard library.

  Thomas is part of the Data Analysis team at European XFEL.
  He has a specific remit to facilitate the use of Jupyter by internal groups
  and visiting researchers,
  but he also contributes to the general software engineering effort working to
  allow convenient, reproducible analysis of data collected at European XFEL.

  Before working as a software engineer, Thomas studied plant biology, gaining
  a PhD from the University of Sheffield in 2013. His work since then has
  continued in close connection with research, at the University of California,
  Berkeley, and the University of Southampton, before joining European
  XFEL.
\end{participant}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:
