\begin{participant}[type=PI,PM=2,gender=female]{Viviane Pons}
  Maître de Conférences at the Laboratoire de Recherche en Informatique, Viviane Pons is a
  young researcher in Algebraic Combinatorics. She defended her thesis in 2013 and has 4
  papers in international journals and 6 communications in international
  conferences, including a talk at PyCon US 2015. She was also invited as a keynote speaker
  at Pycon FR 2018. Since January 2019, she is in the editorial board of the Journal of Open Source Software.
  Before starting her research career,
  she worked for two years in industry as a Java and web developer.

  She discovered \Sage during her first \Sage Days in 2010 and has since been an active user
  and contributor with 10 (co)authored tickets improving the support of combinatorial
  objects in \Sage. She is heavily involved in the promotion of \Sage, participating in
  \Sage Days and running \Sage introduction tutorials or \Sage presentations at various
  conferences. She has also been involved in devloping the project \software{FindStat}
  dedicated to databases in combinatorics.

  Viviane is leading the very successful Community Building and
  Dissemination work package of the European Research Infrastructures
  project OpenDreamKit (2015-2019), in which 66 events (development
  workshops, training sessions, ...) were organized or coorganized,
  with more than a thousand trainees. Viviane herself organized or
  coorganized several of them, including two week-long workshops
  dedicated to women (one in 2017 and one to come in spring 2019).
\end{participant}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:
