\TOWRITE{NT/...}{Finalise}
\TOWRITE{ALL}{Proofread concept and approach pass 2}

\subsection{Concept and Approach}\label{sec:concept}
\eucommentary{5-8 pages}
\eucommentary{
-- Describe and explain the overall concept underpinning the project.
Describe the main ideas, models or assumptions involved. Identify
any trans-disciplinary considerations;
-- Describe and explain the overall approach and methodology, distinguishing, as
appropriate, activities indicated in the relevant section of the work programme, e.g.
Networking Activities, Service Activities and Joint Research Activities, as detailed in
the Part E of the Specific features for Research Infrastructures of the Horizon 2020
European Research Infrastructures (including e-Infrastructures) Work Programme 2014-
2015;\\
-- Describe how the Networking Activities will foster a culture of co-operation between the
participants and other relevant stakeholders.\\
-- Describe how the Service activities will offer access to state-of-the-art infrastructures,
high quality services, and will enable users to conduct excellent research.\\
-- Describe how the Joint Research Activities will contribute to quantitative and qualitative
improvements of the services provided by the infrastructures.\\
-- As per Part E of the Work Programme, where relevant, describe how the project will
share and use existing basic operations services (e.g. authorisation and accounting
systems, service registry, etc.) with other e-infrastructure providers and justify why such
services should be (re)developed if they already exist in other e-infrastructures. Describe
how the developed services will be discoverable on-line.\\
-- Where relevant, describe how sex and/or gender analysis is taken into account in the
project's content.}


Open Science is the principle that science,
in order to be most impactful and socially responsible,
should be done publicly,
with as much of the scientific process and products
accessible, reviewable, and reusable by as many members of the global community as possible.
In the modern age of computational science,
almost all academic fields,
from humanities to social sciences to biology and astronomy are faced with exciting opportunities for Open Science.
As more and more research takes the form of code and/or data,
the opportunity to share, reproduce, and reuse scientific work is greater than ever,
even enabling new forms of interdisciplinary collaboration.

At the same time as we share in these exciting opportunities,
there are corresponding challenges, technical and social,
to making Open Science a practical reality.
We face big questions: If a researcher has code and/or data to publicize, how is that best done?
How do researchers learn best Open Science practices in their field?
How do previously disconnected fields benefit from each other's work as the same computational challenges are faced again and again by different communities?

These are the questions that guide \TheProject.
With so much research being done that wants to be Open,
how can we make Open Science

\begin{enumerate}
    \item as easy as possible to share?
    \item as useful as possible to other researchers and the public?
\end{enumerate}

Our plan for improving access and effectiveness of Open Science can be summarized as:

\begin{enumerate}
    \item improve and maintain common software infrastructure used for Open Science
    \item develop the Jupyter ecosystem to improve capabilities better serve Open Science
    \item guide, validate, and demonstrate our developments through collaboration
          with a wide variety of application domains
    \item enable students and researchers to perform Open Science through
          training and education,
          and improving inclusiveness by focusing these on under-served
          and under-represented communities.
    \item operate services to facilitate Open Science collaborations
          with Jupyter software
\end{enumerate}

\textbf{Why Jupyter?}

\TheProject has chosen to centre its efforts on the Jupyter software ecosystem.
The Jupyter notebook and Jupyter ecosystem is of increasing
importance in computational science and data science, in academia,
industry and services. In addition to supporting high productivity
of researchers, they have great potential to push open science
forward: the notebook provides a complete description of a
computational and data science study, and the notebook can -- in
principle -- be turned into a publication, or can be used to provide
the required computation for a part of a publication, such as a
figure. In this way, the notebook enables reproducibility of complex
tasks with hardly any additional effort on the user side (if used
appropriately). The Binder project allows to execute such notebooks
in tailored computational environments; an aspect of reproducibility
that is not widely supported yet. Furthermore, for users wanting to
connect to a local Jupyter notebook server on their machine, or to
connect to a server somewhere else on the Internet, the users only
need a webbrowser to display the notebook locally. Because of these
characteristics, the Notebook is already planned to become an
important service on the European Open Science Cloud (EOSC), for
example through the EOSC-04 funded PaNOSC project.

\TOWRITE{}{short definition of Jupyter components, mixing code \& prose, etc. }

Because the Jupyter notebook is a web-based application,
it can be deployed at computational facilities or in the cloud,
and can function as the basis for services
exposing computational resources of all kinds to researchers and the public.
Because Jupyter is \textit{interactive},
it enables making scientific results and communications more interactive
than static publications.
The audience can follow their own initiative and ask their own questions of published data
without needing support from the publishing author,
greatly facilitating the \textit{practicality} of Open Science.

\textbf{Jupyter is generic}
\TheProject chose Jupyter because it is Generic.
Jupyter makes no domain-specific or even language-specific assumptions.
Any application where mixing description, code, and results is valuable
can make use of Jupyter.
This broad applicability makes investment in the Jupyter ecosystem extremely effective,
because improvements to Jupyter can serve many communities simultaneously.

Jupyter is built from a collection of standard protocols and file formats.
Jupyter is not just a single, monolithic collection of software,
but a description of how such software can be built.
The result is the ability for a variety of communities and applications
to use pieces of Jupyter for their purposes,
and/or reimplement pieces to meet their needs.

For example:

\begin{enumerate}
    \item The notebook file format is a well-specified JSON document,
    which can be interpreted by many systems.
    This has facilitated the development of different services
    rendering notebooks, e.g. the code hosting website GitHub,
    which renders notebooks for easy viewing by anyone,
    without Jupyter software.
    \item the Jupyter protocol describes how execution is performed,
          which has enabled the development of over one hundred
          kernel implementations in dozens of languages.
    \item output in the Jupyter protocol uses web-standard MIME types,
          enabling any possible format to be an output in a Jupyter notebook.
    \item the JupyterLab extension system provides a system for building applications
          from Jupyter components and others
    \item the Jupyter Widgets provide a system for customizing and extending
          interactivity in Jupyter-based environments
\end{enumerate}

The popularity of Jupyter, with millions of users and hundreds of open source contributors,
indicates the value and impact of this approach.

\textbf{How do we improve Jupyter?}

The benefits of focusing our work on a mature system like Jupyter are

\begin{itemize}
    \item vibrant community ensures health and sustainability
    \item large existing user base maximizes impact of contributions
    \item mature software ecosystem maintains quality software through
          industry standards such as version control, tests, continuous integration,
          stable release cycles, roadmaps, and user support
\end{itemize}

The Jupyter community aims to be inclusive, and \TheProject will continue this effort.
Jupyter is inclusive across a number of axes.
By being applicable across numerous domains,
Jupyter and \TheProject encourage participation from individuals of various interests and backgrounds,
and has taken action to improve diversity in the project
by participating in "Outreachy," a program of paid internships
for individuals from groups that face under-representation, systemic bias, or discrimination.
Jupyter has also operated workshops focused on training contributors from under-represented groups.
In being free, public, open source software, Jupyter and \TheProject
are accessible to as many individuals as possible,
and invites users and contributors beyond origin, nationality, beliefs, orientation.
One area where Jupyter has lacked in this regard is in the User Interface accessibility,
and we will help improve this in \taskref{jupyter-core}{accessibility}.
Additionally, the project will focus some of its workshops in \taskref{education}{workshops}
on under-represented communities.




\begin{verbatim}
Outline notes:

* Carry on with specified protocols and formats so that components can be replaced, combined etc.
* Avoid lock-in to specific technologies (for example JupyterHub not limited to AWS but cloud-provide agnostic way) – thus independent from dominating commercial cloud services provider
* Integrating user input in multiple ways
   * User input at JupyterCon: beginners and experience users to try new version of UI; sessions where recorded and used to improve software (“usability testing”)
   * Co-design: developed by scientists for scientists, but professional software engineers and UX designers involved in the design of the software; [deliberate effort because Jupyter is a tool to teach beginners and specialists]
   * UI is at level of polish that is rarely met in non-commercial applications
\end{verbatim}
