% template for a task
% each task should be added to exactly one workpackage
% in the workpackage task list
\begin{task}[
  title=Prototype European Binder instance and global federation,
  id=eu-binder,
  lead=SRL,
  PM=25,
  wphases={0-48},
  partners={SRL,EGI,WTT,UPSUD}
]
  The team of Project Binder provide a service: https://mybinder.org
  which is public infrastructure powered by the software they develop.
  mybinder.org is used to launch around 80000 "binders" every week and is
  being used by researchers and teachers to make their work reproducible.

  Although mybinder.org is very popular, there are currently only two
  additional public BinderHubs worldwide. This means that there is a limited
  expertise in operating and maintaining such public infrastructure.

  The purpose of this task is to create a community of practice of BinderHub
  operators and operate a European Binder instance.

  Re-executing the code associated with all European Open Access publications
  requires a very large amount of very diverse compute resources. It is
  unrealistic that one BinderHub instance could provide all of these. This is
  why in this task we will work on building a community of practice around
  operating public Binder instances at a research institution.

  Constraints from data protection and privacy mean not all code supporting a
  publications can be made public and/or that data can not be moved outside of
  the EU. This task will work on operating a EU based Binder instance accessible
  to the public. This will mirror the current mybinder.org but be hosted in
  the EU. This European Binder instance will serve as the first partner in the
  global federation of Binder instances.


  %% In 2018 around 2.5million "binders" were launched. In one week of August
  %% around 350 different repositories were launched in a single week. These
  %% numbers show that mybinder.org (and the technology behind it) is seeing fast
  %% adoption in the research and teaching community.


  \begin{compactitem}
  \item Build a community of practice of BinderHub operators. Create a forum
  for Binder operators to exchange experience and tools. Create a report on
  best practices for operation (SRE guide).
  \item Operating a Binder instance in Europe. Find a hoster, use work from
  deployment task, deploy and operate eu.mybinder.org, 
  \item Develop a federation of Binder instances. Leverage the community of
  practice. Solve technical challenges related to federation.
    (\localdelivref{deliv-id})
  \end{compactitem}
\end{task}
