\begin{task}[
  title=Jupyter Interactive Widgets,
  id=jupyter-widgets,
  lead=QS,
  PM=28,
  wphases={0-48!.6},
  partners={SIL,XFEL}
]

The task includes the following activities:

\begin{compactenum}
\item
  Improvements to the core Jupyter Widgets package

  \begin{compactenum}
  \item
    Improve the testing tools for Widget libraries, including means to
    test messaging, schemas, and actual rendering of widgets with a headless
    browser.
  \item
    Modernize of the \emph{@jupyter-widgets\/base} JavaScript package:
    drop \emph{backbone.js} and adopt a more modern MVC framework, support
    streaming of widgets messages to multiple frontends for future support of
    live collaboration.
  \item
    Iterate on the core \emph{@jupyter-widgets\/controls} package. This may
    involve the adoption of a modern framework such as \emph{React.js} for
    the widget view implementation, rather than the current custom implementation.
  \item
    Create new controls for the core Jupyter widgets package such as token
    inputs, typeahead, and tree views. These common controls tend to be implemented
    in several downstream packages, which causes unnecessary duplication of work
    and harms sustainability.
  \end{compactenum}

\item
  Dealing with large widget state

  \begin{compactenum}
  \item Create a generic mechanism for widgets to refer to external data services
  or companion files rather than storing their state entirely in the notebook format
  for offline view.
  \end{compactenum}

\item
  Simplify the authoring of complex GUIs with Jupyter widgets.

  \begin{compactenum}
  \item
    Provide pre-defined Jupyter widget layouts based on the recently
    introduced CSS Grid Layout, with named areas to which widgets can be
    assigned, such as a centra area, left and right tab bars, footer and
    headers, or layouts including areas for logging results on long-running
    tasks.
  \item
    Experiment with the generation of a Jupyter-widgets based GUI from
    a declarative configuration file, or by introspecting a configuration object.
  \end{compactenum}


\item
  Develop interoperable Jupyter widgets for 3d data visualisation.

  \begin{compactenum}
  \item 
    Adopt existing 3d jupyter widget new mechanisms and API of Jupyter widgets

  \item
    Experiment with large dataset visualization and inspection in Jupyter widgets. This will include work on the flexible split of preprocessing between server and widget and the development of data formats for special use cases. 
    
  \item 
    Improve and standardize the interoperablity of  different components and dataformats. 
    
  \item 
    Create comprehensive documentation of 3d widgets with scientifically relevant examples.

  \item 
    Create developer documentation and engage the community for contributions implementing specialisations of the 3d widget.(\localdelivref{k3d-jupyter})
  
  \end{compactenum}

\end{compactenum}

\end{task}
