\begin{sitedescription}{XFEL}
  \label{sitedescription:euxfel}

% PIC:
% see: http://ec.europa.eu/research/participants/portal/desktop/en/orga

% See ../proposal.tex, section Members of the Consortium for a
% complete description of what should go there

  European X-Ray Free-Electron Laser Facility GmbH is a limited
  liability company under German law. At present, 12 countries are
  participating in the project: Denmark, France, Germany, Hungary,
  Italy, Poland, Russia, Slovakia, Spain, Sweden, Switzerland, and the
  United Kingdom.  The company is in charge of the operation and
  construction of the European XFEL, a 3.4 km long X-ray free-electron
  laser facility extending from Hamburg to the neighbouring town of
  Schenefeld in the German federal state of Schleswig-Holstein. Civil
  construction started in early 2009, and the user operation in
  September 2017. With its repetition rate of 27,000 pulses per second
  and a peak brilliance a billion times higher than that of the best
  synchrotron X-ray radiation sources, the European XFEL will allow
  the investigation of still open scientific problems in a variety of
  disciplines (physics, structural biology, chemistry, planetary
  science, study of matter under extreme conditions and many others).


\subsubsection*{Curriculum vitae}

% Curriculum of the personnel at this institution
%
\input{CVs/Hans.Fangohr.tex}
\input{CVs/Sandor.Brockhauser.tex}
\input{CVs/Krzysztof.Wrona.tex}
\input{CVs/Thomas.Kluyver.tex}
%


\begin{participant}[PM=68, type=R]{NN}

We will hire two postdoctoral-level research software engineers (for 68 person
months in total) to carry out the required work for this projet at
European XFEL. They will work under supervision of Hans Fangohr, with
support from Sandor Brockhauser and Krzysztof Wrona for particular
aspects. The employees will either have a scientific background and
significant software engineering expertise, or an education in
computer science and an aptitude to work with scientists on
computational science and data science problems.
\end{participant}

\subsubsection*{Publications, products, achievements}

\begin{compactenum}
\item H.Fangohr, Python for Computational Science and Engineering
  (2018) DOI: 10.5281/zenodo.1411868 \newline
  https://github.com/fangohr/introduction-to-python-for-computational-science-and-engineering
\item H.Fangohr et al., “Data Analysis support in Karabo at European
  XFEL”, Proceedings of International Conference on Accelerator and
  Large Experimental Physics Control Systems 2017, ISBN 978-3-95450-
  193-9, Data Analytics, Barcelona, Spain, TUCPA01 (2017) DOI: 10.18429/JACoW-ICALEPCS2017-TUCPA01
\item H.Fangohr.
\emph{A Comparison of \software{C}, \Matlab and \Python as Teaching Languages in Engineering}
Lecture Notes on Computational Science \textbf{3039}, 1210-1217 (2004)
\item T. Kluyver, B. Ragan-Kelley, F. Perez, B. Granger, M. Bussonier, J. Frederic, K. Kelley, J. Hamrick, J. Grout, S. Corlay et al. Jupyter
\emph{Notebooks: a publishing format for reproducible computational workflows} In 20th International Conference on Electronic Publishing. IOS Press, 2016.
\end{compactenum}

\subsubsection*{Previous projects or activities}

\begin{compactenum}
\item OpenDreamKit (GA No. 676541) Open Digital Research Environment
  Toolkit for the Advancement of Mathematics, participant
\item EOSCpilot (GA No. 739563) The European Open Science Cloud for
  Research Pilot Project, participant
\item PaNOSC (GA No. 823852) Photon and Neutron Open Science Cloud, participant
\end{compactenum}

\end{sitedescription}



%KEY-MORE-TODOS



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:

%  LocalWords:  sitedescription Programme organisations programmes Centres subsubsection
%  LocalWords:  micromagnetic Nmag Fischbacher Franchin Bordignon Fangohr emph textbf
%  LocalWords:  Multiphysics summarised Iridis TFlops Modelling
