\begin{sitedescription}{UIO}

The University of Oslo (UiO) is Norway's oldest institution for research and higher education, with 28,000 students and 6,000 employees. UiO has 8 faculties, 2 museums and several centres. In addition, UiO has 10 Norwegian Centres of Excellence,  is ranked as the world's 62nd university, and has had 5 Nobel prize laureates. UiO aims to become an international hub for the research-based integration of computing into science education and has financed a university-wide hosting service for Jupyter notebooks through JupyterHub  to introduce a computational aspect to all curriculum programs in all science disciplines from bachelor to postdoctoral studies.

The Department of Geosciences of the Faculty of Mathematics and Natural Sciences is the broadest geoscience research-based teaching environment in Norway, and covers a wide range of disciplines from deep mantle processes to atmospheric sciences. It is organised in five sections and an administrative unit and supports two main strategic research initiatives:

- Land-Atmosphere Interactions in Cold Environments (LATICE\footnote{\url{https://www.mn.uio.no/geo/english/research/groups/latice/}})

- Interface Dynamics in Geophysical Flows (EarthFlows\footnote{\url{https://www.mn.uio.no/geo/english/research/groups/earthflows/}})

 

 The geosciences department has several large research projects financed by The Research Council of Norway, EU and Norwegian companies.

\subsubsection*{Curriculum vitae}

% Curriculum of the personnel at this institution. This includes
% to-be-hired people for which there is a tentative candidate.

\input{CVs/Anne.Fouilloux.tex}

%\input{CVs/First.Last.tex}
%\input{CVs/First.Last.tex}
%\input{CVs/First.Last.tex}

% For other to-be-hired person, please include here something like:
% \begin{participant}[type=res,PM=3,salary=5900]{NN}
%  <a _short_ description of the qualifications of whom you want to hire>
% \end{participant}

\subsubsection*{Publications, products, achievements}

\begin{compactenum}
\item Publication ready scientific reports and presentations with Jupyter notebooks (\url{https://annefou.github.io/jupyter_publish/}), Anne Fouilloux, Research Bazaar 2019, DOI 10.5281/zenodo.2548936\footnote{\url{https://zenodo.org/badge/latestdoi/163517733}}

\item Reproducible Research with Interactive Jupyter Dashboards, 2018 (\url{https://annefou.github.io/jupyter_dashboards/}), Ana Costa Conrado, Gladys Nalvarte, Benjamin Ragan-Kelley and Anne Fouilloux, Research Bazaar 2018, DOI 10.5281/zenodo.1168721\footnote{\url{https://zenodo.org/badge/latestdoi/114125668}}

\item Working with Spatio-temporal data in Python, 2017 (\url{https://annefou.github.io/metos_python/}), Anne Fouilloux, DOI 10.5281/zenodo.1165281\footnote{\url{https://zenodo.org/badge/latestdoi/96184802}}
\end{compactenum}

\subsubsection*{Previous projects or activities}

\begin{compactenum}
\item CodeRefinery-2 (2016-2021, \url{https://coderefinery.org}): 

The goal of this project is to teach students and researchers how to write better code and provide research groups with software development e-infrastructure tools to collaboratively develop, review, discuss, test, and share their codes.

CodeRefinery addresses all academic disciplines and try to be as programming language-independent as possible. One of the major tasks of the project is to create new training materials and organize workshops that address students and researchers from any disciplines.

This is a project within the Nordic e-Infrastructure Collaboration (NeIC, \url{https://neic.no}). NeIC is an organisational unit under NordForsk\footnote{\url{https://www.nordforsk.org/en}}.

\item Nordic Collaboration on e-Infrastructures for Earth System Modeling (NICEST, 2017-2019, \url{https://neic.no/nicest}):

This project aims at networking, intensifying existing collaboration, and facilitating 
joint work on very specific topics helping, for example, building up knowledge and
competency, and harmonising certain procedures concerning e-Infrastructure topics.

\item UiOHive (2018-2019, \url{https://uiohive.github.io/Hive/}): 

UiOHive provides a vital and novel competence at the Union of Internet of Things (IoT), Microcontroller / Hardware development, Artificial Intelligence (AI) and Machine Learning, and Data Science to enhance and strengthen collaboration between domains at the application of the aforementioned technologies. and the disciplines with competence to further develop technologies.
The purpose of GEOHive is to establish a central knowledge hub, centered around individuals interested in utilizing IoT technologies, applying AI / ML to data challenges, and sharing knowledge across relevant interdisciplinary domains.

\item LATICE (Land-ATmosphere Interactions in Cold Environments, 2015-2022, \url{https://www.mn.uio.no/geo/english/research/groups/latice/}): 
LATICE aims to advance the knowledge base concerning land atmosphere interactions and their role in controlling climate variability and climate change at high northern latitudes.

\item EarthFlows (2015-2002, Interface Dynamics in Geophysical Flows, \url{https://www.mn.uio.no/geo/english/research/groups/earthflows/}): 
The dynamics of interface processes during flows on Earth, including the geosphere, the hydrosphere, the cryosphere, and the atmosphere, including the behavior of the complex interfaces separating ‘Fluid Earth’ from ‘Solid Earth’.

The goal for the EarthFlows project is to provide fundamentally new understanding of the dynamics of fluid-solid interfaces for a number of important geophysical systems.

\end{compactenum}

\subsubsection*{Significant infrastructure}

\begin{compactenum}

\item Infrastrcture as a Service (http://www.uh-iaas.no/): the University of Oslo is part of the Norwegian Cloud Infrastructure for Research and Education and provide researchers with compute and storage medium-size resources. These include multi-GPUs clusters for big data analysis. The department of Geosciences is heavily relying on this services both for teaching and research work.

\item UNINETT Sigma-2 (https://sigma2.no): UNINETT Sigma2 manages the national infrastructure for computational science in Norway and offers services in High Performance Computing (HPC) and Data Storage. The services are organized into infrastructural activities, financed by the Research Council of Norway and the Sigma2 consortium partners, which are the universities in Oslo, Bergen, Trondheim and Tromsø.

Services are freely available to individuals and groups involved in  research and education at Norwegian universities and colleges, and other organizations and project funded with public money. Cost efficient development, procurement, coordination and operation of the national e-infrastructure for research and education is the main focus for Sigma2.
\end{compactenum}

\end{sitedescription}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:
