\begin{sitedescription}{WTT}
\label{sitedescription:euxfel}

Wild Tree Tech GmbH is a limited liability company under Swiss law established
in 2017. Its business is built on three pillars: custom data driven software products,
hosted JupyterHub services and training courses in machine-learning techniques.

Clients include NGOs, companies, hospitals, universities and UN organisations
from Switzerland, France and the USA.

Wild Tree Tech employees co-create, co-lead and contribute to international
open-source projects used by thousands people who use computers for teaching
and data-science. The Binder Project creates, advances, and promotes
open technology that makes it easy for people to connect their data
science communications, educational materials, and scientific work with
computational environments where their work can be run and shared with others.
The Binder project operates a public infrastructure at https://mybinder.org.
Wild Tree Tech contributes resources for operation and maintenance of this
free public service.



\subsubsection*{Curriculum vitae}

% Curriculum of the personnel at this institution. This includes
% to-be-hired people for which there is a tentative candidate.

\input{CVs/Tim.Head.tex}

% For other to-be-hired person, please include here something like:
\begin{participant}[type=res,PM=24,salary=9580]{NN} %% salary in CHF
  We will hire a software engineer with experience working in distributed teams
  and open-source projects. They will have experience in using Kubernetes and
  Jupyter.
\end{participant}

\subsubsection*{Publications, products, achievements}

\begin{compactenum}
\item Hub Hero, JupyterHubs for workshops, lecture courses and institutions. Harness the power of Jupyter notebooks for classes allowing teachers to teach interactively without needing tech support.
\end{compactenum}

\subsubsection*{Previous projects or activities}

\begin{compactenum}
\item Binder
\end{compactenum}

\subsubsection*{Significant infrastructure}
\begin{compactenum}
\item mybinder.org, Wild Tree Tech helps operate a BinderHub available to the public that allows anyone to turn a Git repository into a collection of interactive Jupyter notebooks. This service is available for free and was used to launch over 2.5million notebooks in 2018 alone.
\end{compactenum}

\end{sitedescription}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:
